Towards the near-infrared detection of brown dwarf companions: Exploring methods to detect low mass stellar companions from blended spectra \thanks{Based on observations collected at the European Organisation for Astronomical Research in the Southern Hemisphere under ESO programme 089.C-0977(A)}

### 2018-07-20 nir_companions.tex
Update on Overleaf.
Move figure

\subsubsection{Data reduction}
\label{subsubsec:reduction}
The observations were reduced using a custom reduction pipeline~\citep{figueira_radial_2010} with some of the parameters altered to better suit the \textit{K}-band instead of the \textit{H}-band setting it was originally designed for. Written in IRAF's CL\footnote{IRAF is distributed by the National Optical Astronomy Observatories, which are operated by the Association of Universities for Research in Astronomy, {Inc.}, under cooperative agreement with the National Science Foundation.}~\citep{tody_iraf_1993} it provides for automated dark and non-linearity corrections (using the non-linearity coefficients provided by ESO), as well as the flagging and replacement of bad pixels. The images were corrected from sensitivity variations by dividing by a flat-field corrected from the blaze function effect. The nodding pairs were mutually subtracted and the order tracing was fitted by cubic splines.

@@

\begin{figure}
    \includegraphics[width=\hsize]{images/Bad_pixel_replacement.pdf} % chktex 8
    \caption{Example of an artifact in the optimally extracted spectra. The top panel contains the 8 normalized nod spectra after optimal extraction, while the middle panel shows the rectangular extraction for the exact same spectra. A vertical offset is included between each spectra. A single large spike in the seventh nod (pink) near pixel 230 creates a wide and noticeable artifact in the optimal extraction. The bottom panel shows the difference between a combined spectrum using the optimal nods only and a combined spectrum in which the seventh nod is replaced with its rectangular counterpart. The nod spectra are in observation order from top to bottom.}
    \label{fig:nod_artifacts}
\end{figure}

@@

\subsection{\(\chi^{2} \) method}
\label{subsec:chi2}
The well known \(\chi^{2} \) technique measures the weighted sum of the squared deviation between the observation (\({O}_{i}\)) and the computed models (\(C_{i}\)), with the minimum \(\chi^2\) value representing the best-fit parameters.
\[\chi^{2} = {\Sigma}_i { (O_{i} - C_{i})}^2 / {\sigma}_{i}, \] where \({\sigma}_{i}\) is the error on each measurement. We estimate the \(\sigma\) of each spectrum using the \(\beta\sigma\) method~\citep{czesla_posteriori_2018}, using the MAD (median absolute deviation about the median) robust estimator, an order of approximation of 5, and a jump parameter of 2. We apply the same \(\sigma\) value to all points \({\sigma}_{i} = \sigma\). The \(\beta\sigma\) method provided \(\sigma\) estimates for the target spectra which correspond inversely to signal-to-noise ratios between 100--500.

>>>>

\subsubsection{Data reduction}
\label{subsubsec:reduction}
\begin{figure}
    \includegraphics[width=\hsize]{images/Bad_pixel_replacement.pdf} % chktex 8
    \caption{Example of an artifact in the optimally extracted spectra. The top panel contains the 8 normalized nod spectra after optimal extraction, while the middle panel shows the rectangular extraction for the exact same spectra. A vertical offset is included between each spectra. A single large spike in the seventh nod (pink) near pixel 230 creates a wide and noticeable artifact in the optimal extraction. The bottom panel shows the difference between a combined spectrum using the optimal nods only and a combined spectrum in which the seventh nod is replaced with its rectangular counterpart. The nod spectra are in observation order from top to bottom.}
    \label{fig:nod_artifacts}
\end{figure}

The observations were reduced using a custom reduction pipeline~\citep{figueira_radial_2010} with some of the parameters altered to better suit the \textit{K}-band instead of the \textit{H}-band setting it was originally designed for. Written in IRAF's CL\footnote{IRAF is distributed by the National Optical Astronomy Observatories, which are operated by the Association of Universities for Research in Astronomy, {Inc.}, under cooperative agreement with the National Science Foundation.}~\citep{tody_iraf_1993} it provides for automated dark and non-linearity corrections (using the non-linearity coefficients provided by ESO), as well as the flagging and replacement of bad pixels. The images were corrected from sensitivity variations by dividing by a flat-field corrected from the blaze function effect. The nodding pairs were mutually subtracted and the order tracing was fitted by cubic splines.

@@

@@

\subsection{\texorpdfstring{\(\chi^{2}\)} method}
\label{subsec:chi2}
The well known \(\chi^{2} \) technique measures the weighted sum of the squared deviation between the observation (\({O}_{i}\)) and the computed models (\(C_{i}\)), with the minimum \(\chi^2\) value representing the best-fit parameters.
\[\chi^{2} = {\Sigma}_i { (O_{i} - C_{i})}^2 / {\sigma}_{i}, \] where \({\sigma}_{i}\) is the error on each measurement. We estimate the \(\sigma\) of each spectrum using the \(\beta\sigma\) method~\citep{czesla_posteriori_2018}, using the MAD (median absolute deviation about the median) robust estimator, an order of approximation of 5, and a jump parameter of 2. We apply the same \(\sigma\) value to all points \({\sigma}_{i} = \sigma\). The \(\beta\sigma\) method provided \(\sigma\) estimates for the target spectra which correspond inversely to signal-to-noise ratios between 100--500.
